diffusion, websites with 1 pc

### 2023-03-22 src/level_lisa_la.Rmd
file system

```{r}
path.out <- paste0(path, "/outputs/lisa/morani_la.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  #kable() %>% 
  write_csv(path.out)

>>>>

```{r}
path.out <- paste0(path, "/outputs/lisa/morani_la.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  #kable() %>% 
  write_csv(path.out)
```

### 2023-03-22 src/level_lisa_oa.Rmd
file system

path.out <- paste0(path, "/outputs/lisa_level_pc", n, "_oa") # for unique PC
#path.out <- paste0(path, "/outputs/lisa_level_pc", m, "_oa")  # for multiple PC

@@

```{r}
path.out <- paste0(path, "/outputs/morani_oa.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  kable() #%>% 
  #write_csv(path.out)

@@

path.out <- paste0(path, "/outputs/gini_oa.csv")
gini.df %>% write_csv(path.out)
```

@@

path.out <- paste0(path,"/outputs/rsq_dist_london_oa.png")
ggplot(dens.London) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to London on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_london_oa.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
#ggplot(out.model, aes(x=year, y = estimate)) +  
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to London on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/rsq_dist_city_oa.png")
ggplot(dens.distMet) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest city on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_city_oa.png")
ggplot(out.modelMet, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/rsq_dist_centre_oa.png")
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest retail centre on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_centre_oa.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest retail centre on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

```{r}
path.out <- paste0(path, "/outputs/r2_all_oa.csv")

>>>>

path.out <- paste0(path, "/outputs/lisa/lisa_level_pc", n, "_oa") # for unique PC
#path.out <- paste0(path, "/outputs/lisa/lisa_level_pc", m, "_oa")  # for multiple PC

@@

```{r}
path.out <- paste0(path, "/outputs/lisa/morani_oa.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  #kable() %>% 
  write_csv(path.out)
```

@@

path.out <- paste0(path, "/outputs/lisa/gini_oa.csv")
gini.df %>% write_csv(path.out)
```

@@

path.out <- paste0(path,"/outputs/lisa/rsq_dist_london_oa.png")
ggplot(dens.London) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to London on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/lisa/b_dist_london_oa.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
#ggplot(out.model, aes(x=year, y = estimate)) +  
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to London on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/lisa/rsq_dist_city_oa.png")
ggplot(dens.distMet) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest city on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/lisa/b_dist_city_oa.png")
ggplot(out.modelMet, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/lisa/rsq_dist_centre_oa.png")
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest retail centre on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/lisa/b_dist_centre_oa.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest retail centre on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

```{r}
path.out <- paste0(path, "/outputs/lisa/r2_all_oa.csv")
